Observing Earth as an Exoplanet with \TESS: Photometric Mapping of Surface Features in Reflected Light

### 2019-05-01 tex/ms.tex
changes to abstract and conclusions

\begin{abstract}
\todo{(TO BE CHANGED:)}
To date, a handful of exoplanets have been photometrically mapped using phase-modulated 
reflection or emission from their surfaces, but the small amplitudes 
of such signals have limited previous maps almost exclusively to coarse dipolar
features on hot giant planets. 
In this work, we uncover a signal using recently released data from the Transiting 
Exoplanet Survey Satellite (\TESS), which we show corresponds to time-variable reflection 
from a terrestrial 
planet with a rotation period of $0.9972696$ days. 
Using a spherical harmonic-based reflection model developed as an extension of 
the \starry package, we are able to reconstruct the surface features of this rocky 
world. We recover a time-variable albedo map of the planet including persistent 
regions which we interpret as oceans and cloud banks indicative of continental features. 
We argue that this planet represents the most promising detection of a habitable 
world to date, although the potential intelligence of any life on it is yet to 
be determined.
\href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faGithub}
\end{abstract}

@@

We detect three large scale bright regions near
the equator of the planet, associated with persistent cloud structures
at longitudes of $-60^\circ$, $+30^\circ$, and $+90^\circ$, which
likely track continents. Pronounced dark features are identified
at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
significant latitudinal extent, likely corresponding to oceans. Because of the
vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
high latitudes on the planet, although this may change with upcoming
sectors.

We fit Earth with both static and time-variable albedo maps. 
We find tentative evidence for variability in Earth's cloud coverage over 
the course of Sector 1 observations. 
Upcoming observations with \TESS will yield further information on 
the time variability of surface features on Earth on a variety of timescales.

>>>>

\begin{abstract}
To date, a handful of exoplanets have been photometrically mapped using phase-modulated 
reflection or emission from their surfaces, but the small amplitudes 
of such signals have limited previous maps almost exclusively to coarse dipolar
features on hot giant planets. 
With future instruments, more detailed mapping of terrestrial planets may become possible, 
but significant challenges will remain in analyzing and interpreting these data. 
In this work, we extract a rotationally-modulated reflected light curve of the Earth 
from the time-variable background flux in data from the Transiting Exoplanet Survey Satellite (\TESS).
We treat these data as an unknown exoplanet and reconstruct surface features  
using a spherical harmonic-based reflection model developed as an extension of 
the \starry package. We recover a time-variable albedo map including persistent 
regions indicative of Earth's major oceans and cloud banks. 
Our results suggest that the recovery of surface features on a terrestrial exoplanet
from reflected-light photometric monitoring will be possible, but will require
a considerable investment of observing time to achieve the high cadence and 
long time baseline needed.
\href{https://github.com/rodluger/earthshine}{\color{linkcolor}\faGithub}
\end{abstract}

@@

We detect three large scale bright regions near
the equator of the planet at longitudes of 
$-60^\circ$, $+30^\circ$, and $+90^\circ$, 
which we interpret as persistent cloud structures 
near the Andes, sub-Saharan Africa, and the South Asian monsoon. 
Pronounced dark features are identified
at longitudes of $\pm 180^\circ$, $-30^\circ$, and $+60^\circ$ with
significant latitudinal extent, likely corresponding to 
the Pacific, Atlantic, and Indian Oceans. Because of the
vantage point of \TESS during Sectors 1 and 2, we are not sensitive to
high latitudes on the planet, although this may change with upcoming
sectors.

We fit Earth's light curve with both static and time-variable albedo maps. 
We find tentative evidence for variability in Earth's cloud coverage over 
the course of Sector 1 observations. 
Upcoming observations with \TESS will yield further information on 
the time variability of surface features on Earth on a variety of timescales.
